---
title: "R Notebook to create a Source-Of-Flow attribute in REC2 which matches the REC1 "SRC_OF_FLW" attribute.
output: html_notebook
---

Tim Kerr
Rainfall.NZ for LWP.

April 2020

This has been prepared based on the report:
Fraser, C., 2009, REC3 ‘Source of Flow’ and ‘Geology’ classifications, Derivation method and comparison with REC1 definitions. Confidential client report for Environment Southland by Land Water People Ltd. LWP Client Report 2019-06. LWP, Christchurch.

Outline
Source of flow is a 5 class classification for rivers where the classes are:
Lowland, Hill country, Mountains, Glacial Mountains and Lakes.
The original source data and methods of preparation have been lost to antiquity, so emulating the classes for new versions of REC is non-trivial.
Caroline Fraser (LWP) developed a method of deriving the classes based on watershed average elevation, upstream average elevation, watershed area, upstream area and stream order, attributes reasonably easily derived for any new REC version.

Caroline developed the process to generate REC3 source of flow.

This script is a replication of Caroline's work except for REC2

Load libraries and source functions
```{r}
if (!require(foreign)) install.packages("foreign"); library(foreign)                #enables loading of a DBF file
if (!require(dplyr)) install.packages("dplyr"); library(dplyr)                #enables left_join function
if (!require(plyr)) install.packages("plyr"); library(plyr)                #Has the join function
if (!require(rgdal)) install.packages("rgdal"); library(rgdal)                #used for spatial processing
if (!require(rgeos)) install.packages("rgeos"); library(rgeos)                #used for spatial processing
if (!require(raster)) install.packages("raster"); library(raster)                #used for spatial processing
if (!require(tidyr)) install.packages("tidyr"); library(tidyr)                #used for pivot_wider function

```

Some useful functions
```{r}
#These are slight variations aggregation functions commonly used by LWP. I think the difference was required because I misinterpreted the IDnew parameter to the functions.
#These functions requires preparation of an IDSort vector, and a Reach vector.
#
# Downstream Aggregation of a single variable
#
#Example call: MyREC$PloadSUM<-DstAggr_OneVar(IDSort=MyREC$IDSort,Aggrvar=MyREC$Pload,Reach=Reach,IDnew=match(MyREC$NZReach,IDs))
DstAggr_OneVar=function(IDSort=NULL,Aggrvar=NULL,Reach=Reach,IDnew=NULL){
  #Note: the use of IDnew is because my verisons of IDsort and Reaches are for the whole country.  IDnew allows subsets of the country to be processed
  val<-sort(unique(IDSort))                                 #Determines the order to do the calculations
  OUTPUT<-vector(mode="numeric",length=length(Reach)) *NA                                      #Initiate output matrix
  
  OUTPUT[IDnew[which(IDSort==1)]]<-Aggrvar[which(IDSort==1)]  #Fill in the 1st order streams (which are just the local values)
  print("Start accumulation....")
  for (i in 2:length(val)){
    index2<-which(IDSort==val[i])
    index<-IDnew[index2]
    for (j in 1:length(index)){
      OUTPUT[index[j]]<-sum(OUTPUT[Reach[[index[j]]]])+Aggrvar[index2[j]] 
    } 
  }
  OUTPUT<-OUTPUT[IDnew];OUTPUT[OUTPUT==0]<-NA
  return(OUTPUT)
}


######################################################################################
#  Downstream Aggregation with area weighting (gives UPST average)                   #
######################################################################################

DstAggr_AreaAvg=function(IDSort=NULL,Aggrvar=NULL,segArea=NULL,upstArea=NULL,Reach=Reach,IDnew=NULL){
  
  val<-sort(unique(IDSort))                                 #Determines the order to do the calculations
  OUTPUT<-vector(mode="numeric",length=length(Reach)) *NA   #Initiate output matrix
  OUTPUT[IDnew[which(IDSort==1)]]<-Aggrvar[which(IDSort==1)] #Fill in the 1st order streams (which are just the local values)
  print("Start accumulation....")
  for (i in 2:length(val)){
    index2<-which(IDSort==val[i])
    index<-IDnew[index2]
    for (j in 1:length(index)){
      
      OUTPUT[index[j]]<-(sum(OUTPUT[Reach[[index[j]]]]*upstArea[Reach[[index[j]]]])+Aggrvar[index2[j]]*segArea[index2[j]])/upstArea[index2[j]]  #This ammended version worked
      #OUTPUT[index[j]]<-(sum(OUTPUT[Reach[[index[j]]]]*upstArea[[IDnew[index[j]]]]+Aggrvar[index2[j]]*segArea[index2[j]])/upstArea[index2[j]]  #This version did not work
    } 
  }
  OUTPUT<-OUTPUT[IDnew];OUTPUT[OUTPUT==0]<-NA
  return(OUTPUT)
}
```


set directories and file names
```{r}
ProjectDirectory <- "D:\\Projects\\LWP\\SouthlandRegionalForumModelling"
DataDirectory <- file.path(ProjectDirectory,"Data")
GISDirectory <- file.path(DataDirectory,"GIS")

WatershedsDBFFile <- file.path(GISDirectory,"ES_REC2_Watersheds","ES_REC2_Watersheds.dbf")
RiverlinesDBFFIle <- file.path(GISDirectory,"ES_REC2_Riverlines","ES_REC2_Riverlines.dbf")

REC2WaterShedsFile <- "ES_REC2_Watersheds" #This is an ESRI polygon shapefile

REC1ToREC2File <- file.path(GISDirectory,"REC1REC2Intsn","REC1REC2Intsn.dbf")

REC2FUnctions <- file.path(ProjectDirectory,"R","CASM_Southland","GeneralFunctionsForREC2_v10.R")

REC1UtilityFile <- file.path(DataDirectory,"REC1Utility.rdata")  #This contains a dataframe called REC1Utility, which has a whole bunch of REC1 attributes, including "SRC_OF_FLW" which is what we are trying to replicate in REC2

REC1WithESWaterPlanAttributes <- file.path(GISDirectory,"REC1WaterPlan","REC1WaterPlan.dbf")

LRIFile      <- "NZLRIClip"  #This is an ESRI polygon file

TopRockRasterFile <- file.path(GISDirectory,"TopRock_Raster_30m2.tif")
BaseRockRasterFile <- file.path(GISDirectory,"BaseRock_Raster_30m2.tif")

LRIToHardSoftLakeLookUpTableFile <- file.path(DataDirectory,"LRItoREC_HardSoftLake.csv")

DownstreamAggregationAttributeFile <- file.path(DataDirectory,"REC2DownStreamAggrData.rds")  #This is an R file that contains a list with the Reach and IDSort lists within it, needed for downstream aggregation of the SouthlandREC2 data, ordered according to the "SouthlandREC2_tk.csv" file, which is the same as the REC2Riverlines data 

#File with all the REC2 reaches that intersect a polygon in the Land Resources Inventory with a TopRock attribute of "Lak". This was externally prepared in QGIS
REC2LakeFile <- file.path(DataDirectory,"SouthlandREC2ReachesWithLakes.csv")

#File with all the REC2 reaches that are lakes or downstream of lakes and their watershed intersects with an REC1 watershed with a source of flow class of "lk"
REC2LakesCorrectedtoREC1File <- file.path(DataDirectory, "REC2dstLakesMatchedtoREC1SOFLakes.csv")

#File with Water Plan classes derived by using the REC2 to REC1 reach linkage
REC2WaterPlanDerivedDirectlyFromREC1 <- file.path(DataDirectory,"REC2WaterPlanV0.csv")

#File with REC2 riverline vertices and associated REC1 Natural 30 m raster values
REC2NaturalRiverVerticesFile <- file.path(DataDirectory,"REC2RiverlineVerticesInNaturalArea.csv")
```


Load the REC2 data Southland
```{r}
#This is an REC data file with up catchment average elevation already calculated.
SouthlandREC2 <- read.table(file.path(DataDirectory,"SouthlandREC2_tk.csv"),sep=",", stringsAsFactors = FALSE, header = TRUE)

REC1ToREC2All <- read.dbf(REC1ToREC2File)

load(REC1UtilityFile)   #This provides the REC1Utility data frame
#Cut it down to Southland
SouthlandREC1 <- REC1Utility[REC1Utility$Region == "S",]
rm(REC1Utility)



#Load the REC2 Watersheds polygon shape file
REC2Watersheds <- readOGR(dsn =file.path(GISDirectory,REC2WaterShedsFile),
                           layer = REC2WaterShedsFile, stringsAsFactors = FALSE)
REC2Watersheds <- spTransform(REC2Watersheds,CRS("+init=epsg:2193") )

#If everything needs to be recreated then start with a new SouthlandREC2:
# #Load the attribute data for the ESRI vector data for the riverlines and the watersheds. They have been pre-processed in QGIS to have mean elevation of each watershed. This was done using focal statistics tool.
REC2Riverlines <- read.dbf(RiverlinesDBFFIle)
# 
# SouthlandREC2 <- join(REC2Riverlines,REC2WaterSheds@data[,c("nzsegment","ElevAve")], by="nzsegment")

#Load the IDSort and Reach objects for REC2, needed for downsrtream aggregation
DownstreamAggregationData <- readRDS(DownstreamAggregationAttributeFile)
```


If it is necesary to recreate the aggregated upstream mean elevation attribute, that can be done here.
```{r}
# #Create the "IDSort" and "Reach" lists that are needed for the downstream aggregation function.
# 
# #~~~~~~~~~~~~~~~~~Create Reach~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# # Start with creating the Reach list, which has a list for each reach containing the reaches that are immediately upstream.
# # At the same time create a vector of the number of immediately-upstream reaches for each reach.
# Reach<-list()
# LReach<-seq(1,nrow(SouthlandREC2),1)
# for (i in 1:nrow(SouthlandREC2)){
#   Reach[[i]]<-which(SouthlandREC2$TO_NODE==SouthlandREC2$FROM_NODE[i])    
#   LReach[i]<-length(Reach[[i]])
# }
# 
# #~~~~~~~~~~~~~~~~~Create IDSort~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# #Go through the reaches from top to bottom and generate "IDSORT"  which gives the order that they shold be processed.
# #This takes some time (an hour?!). This is needed to work the downstream aggregation function above
# IDRiver <- seq(1,nrow(SouthlandREC2),1)            
# IDSort  <- IDRiver*0 
# num     <- 1  #First assign a "1" to the most upstream reaches
# IDSort[LReach==0]<-num
# in1<-sum(IDSort)  
# num<-num+1 #Assign the order (IDSort) that the reaches must be calculated in
# index  <-which(IDSort==0 & SouthlandREC2$StreamOrde <= num)
# index2 <-which(IDSort!=0) #These are the most upstream catchments
# 
# while (nrow(SouthlandREC2)-in1>0) {
#   ind<-seq(1,length(index),1)
#   Lmatch<-unlist(lapply(ind,function(x) length(which(!is.na(match(Reach[[index[x]]],index2))==T))))
#   i2<-which(LReach[index]==Lmatch)
#   IDSort[index[i2]]<-num
#   in1<-in1+length(i2)   
#   num<-num+1
#   index<-which(IDSort == 0 & SouthlandREC2$StreamOrde <= num)
#   index2<-which(IDSort != 0) #These are the most upstream catchments    
#   print(in1/nrow(SouthlandREC2)*100)
# } 
# 
# #Save the IDSort and Reach information for later
# DownstreamAggregationData <- list(IDSort=IDSort,Reach=Reach)
# saveRDS(DownstreamAggregationData, file= DownstreamAggregationAttributeFile)




#Use the downstream aggregation function to get the upstream average elevation for each reach

# accumulate area averaged elevation
SouthlandREC2$upstElev <- DstAggr_AreaAvg(IDSort=DownstreamAggregationData[["IDSort"]], Aggrvar=SouthlandREC2[, "ElevAve"],segArea = SouthlandREC2$CATAREA,upstArea = SouthlandREC2$CUM_AREA, Reach=DownstreamAggregationData[["Reach"]], IDnew=seq(1, length(SouthlandREC2$nzsegment),1))

#Accumulate area to test
#SouthlandREC2$AccumArea <- DstAggr_OneVar(IDSort=IDSort, Aggrvar=SouthlandREC2[, "CATAREA"], Reach=Reach, IDnew=seq(1, length(SouthlandREC2$nzsegment),1))

#Save the table for later 
write.table(SouthlandREC2,file.path(DataDirectory,"SouthlandREC2_TK.csv"),row.names = FALSE, quote = FALSE, sep=",")

```


The next step is to establish the elevation threshold that provides the best match for classification to the REC1 source of flow attribute
Externally an REC1 to REC2 allignment has been carried out by intersecting (in QGIS, ignoring the polygons with topological errors) their respective watershed files
The REC1 to REC2 is a many to many relationship, but it is necesary to develop a 1 to 1 relationship. 
This is done in two steps.
1/ For each REC2 ID, select the REC1 ID that intersects with the largest area. This step appears to be missing from Caroline's report.
2/ For each REC1 ID, select the REC2 ID with the largest upstream area.
The REC2 attributes can then be joined to the REC1 ID's.
```{r}
#Pare down the REC1 to REC2 data (many to many) based on the area of intersection to give a REC2 to REC1 1 to many relationship
REC2toManyREC1<-ddply(REC1ToREC2All,.(nzsegment),summarise,NZREACH=NZREACH[which.max(Area)])

#Add upstream area attribute to the REC1-to-REC2 table
REC2toManyREC1PlusCumArea<-join(REC2toManyREC1,SouthlandREC2[,c("nzsegment","CUM_AREA")])

#Select just the largest REC2 for each REC1 to give a 1 to 1 relationship
REC1toREC2<-ddply(REC2toManyREC1PlusCumArea,.(NZREACH),summarise,nzsegment=nzsegment[which.max(CUM_AREA)])

#Tack on all the other REC2 attributes, and the REC1 attributes that will be needed
REC1WithREC2 <- join(REC1toREC2,SouthlandREC2[,c("nzsegment","StreamOrde","CATAREA","CUM_AREA","upstElev")],type="left")
REC1WithREC2 <- left_join(REC1WithREC2, SouthlandREC1[,c("NZReach","SRC_OF_FLW")],by=c("NZREACH"="NZReach"))

#Output the REC1ToREC1 table but only for source of flow of lowland, hill and mountain

REC1WithREC2Output<-REC1WithREC2[REC1WithREC2$SRC_OF_FLW %in% c("L","H","M"),c("NZREACH","StreamOrde","SRC_OF_FLW","CATAREA","CUM_AREA","nzsegment","upstElev")]
write.csv(REC1WithREC2Output,file=file.path(DataDirectory,"REC2toREC1.csv"), row.names = FALSE)
```


Externally (in REC1and REC2.xlsx) the "REC2toREC1.csv" data has been used to develop:
a relationship between the upstream average elevation threshold needed to allocate the Lowland class and log10 of upstream catchment area.
An upstream average elevation threshold for the mountain class.
This was achieved by minimising the difference between the total area of the REC1 "L","H",and "M" Source-of-Flow attributes of each REC2 segment (assigned using the REC1 to REC2 linkage derived above) and the area based on the thresholded upstream area-averaged elevation. This was done for each stream order, then a polynomial relationship found.
This can be used on the REC2 data to generate lowland classes
```{r}
#REC3$LCutoff<-(-1.2141*(log10(REC3$upstArea))^3 + 33.011*(log10(REC3$upstArea))^2 - 261.91*(log10(REC3$upstArea)) + 1045.4) #Original for REC3

SouthlandREC2$LCutoff<-(-1.2709*(log10(SouthlandREC2$CUM_AREA))^3 + 38.021*(log10(SouthlandREC2$CUM_AREA))^2 - 327.11*(log10(SouthlandREC2$CUM_AREA)) + 1264.7) 
SouthlandREC2$SRC_OF_FLW_new<-"L"
SouthlandREC2$SRC_OF_FLW_new[SouthlandREC2$upstElev>SouthlandREC2$LCutoff]<-"H"
SouthlandREC2$SRC_OF_FLW_new[SouthlandREC2$upstElev>980]<-"M"           #The REC3 threshold was 990.

write.table(SouthlandREC2,file.path(DataDirectory,"SouthlandREC2_TK.csv"),row.names = FALSE, quote = FALSE, sep=",")
```

I also need the GEOLOGY classes.
This comes from a reclassification of the Land Resources Inventory's "TopRock" and "Baserock" attributes.
The reclassification to the REC1 GEOLOGY class is from Snelder (2010) Table 2.5 and reproduced in
https://harrcons.sharepoint.com/:x:/r/sites/SouthlandRegionalCouncilJointProjects/Shared%20Documents/Analysis/GIS/LRItoREC_Geol2.csv?d=w55303f32153e494893f6c37c08890d8d&csf=1&web=1&e=27RkTz
This has already been done with two 30m raster files generated.
Externally in QGIS these rasters were sampled at the REC2 watersheds (selecting the raster cell value that is the majority within each watershed)
QGIS proves to be much faster than R for these operations. This needs investigation...

The reclass from GEOLOGY to "hard" soft" is from:
https://harrcons.sharepoint.com/:w:/r/sites/SouthlandRegionalForumModelling/Shared%20Documents/Data/WaterPlanClassesREC2/how%20the%20management%20classes%20were%20mapped.docx?d=w5372cb3cb8a64d6e88220080ffa092e5&csf=1&web=1&e=8WGSrE

```{r}
#Load the GEOLOGY-reclassed-LRI
#LRI <- readOGR(dsn =file.path(GISDirectory,LRIFile),
#                           layer = LRIFile, stringsAsFactors = FALSE)
#LRI <- spTransform(LRI,CRS("+init=epsg:2193") )

#Load the TopRock and BaseRock rasters. Note that the classes are:
GEOLOGYClasses <- c("Al","HS","M","Pl","SS","VB","Lk","Ice")
TopRock <- raster(TopRockRasterFile)
BaseRock <- raster(BaseRockRasterFile)

#Create a "GEOLOGY" raster based on TopRock, except with BaseRock values when TopRock is M
GEOLOGY <- TopRock
GEOLOGY[which(values(GEOLOGY) == 3)] <- BaseRock[which(values(GEOLOGY) == 3)]
crs(GEOLOGY) <- CRS("+init=epsg:2193")

#remove the TopRock and BaseRock rasters to save space
rm(TopRock)
rm(BaseRock)



#Create a new "GEOLOGY" attribute based on the TopRock (TRMajority) attribute, except where it is "M" in which case use the BaseRock (BRMajority) attribute
REC2Watersheds$GEOLOGY <- REC2Watersheds$TRmajority
REC2Watersheds$GEOLOGY[which(REC2Watersheds$GEOLOGY == 3)] <- REC2Watersheds$BRmajority[which(REC2Watersheds$GEOLOGY == 3)]
  
##Convert all the NA types to "M"
#REC2GEOL$GEOLOGY[is.na(REC2GEOL$GEOLOGY)] <- "M"

#Make GEOLOGY a factor and set the levels to their REC geological classes
REC2Watersheds$GEOLOGY <- as.factor(REC2Watersheds$GEOLOGY)
levels(REC2Watersheds$GEOLOGY) <- GEOLOGYClasses <- c("Al","HS","M","Pl","SS","VB","Lk","Ice")

#It is now necesary to find the total upstream area of the geology class.
#This was carried out on a subset of the data
#an area weighted downstream aggregation for each class. To enable this, the GEOLOGY class needs to be pivoted, with a value of 1 for each reach.
REC2GEOL <- REC2Watersheds@data[,c("nzsegment","GEOLOGY")]

REC2GEOL$values <- 1
REC2GEOL_Wide <- pivot_wider(REC2GEOL,id_cols=nzsegment,names_from=GEOLOGY,values_from=values,values_fill = list(values=0))


#Add on the catchment areas and the cumulative catchment area
REC2GEOLWideWithAreas <- join(SouthlandREC2[,c("nzsegment","CATAREA","CUM_AREA")],REC2GEOL_Wide,type="left")

#Carry out downstream area-weighted aggregation for each geological class
# accumulate area averaged elevation
REC2AreaWeightedGeology <- data.frame(sapply(c("Al","HS","M","Pl","SS","VB","Lk","Ice"), function(GEOLClass) {
  AreaWeights <- DstAggr_AreaAvg(IDSort=DownstreamAggregationData[["IDSort"]], Aggrvar=REC2GEOLWideWithAreas[, GEOLClass],segArea = REC2GEOLWideWithAreas$CATAREA,upstArea = REC2GEOLWideWithAreas$CUM_AREA, Reach=DownstreamAggregationData[["Reach"]], IDnew=seq(1, length(REC2GEOLWideWithAreas$nzsegment),1))
}))

#Add a class for any reaches with all NA's
REC2AreaWeightedGeology$Unknown <- NA
REC2AreaWeightedGeology$Unknown[!complete.cases(REC2AreaWeightedGeology)] <- 1

#Find the majority class
REC2AreaWeightedGeology$majorityclass <- colnames(REC2AreaWeightedGeology)[apply(REC2AreaWeightedGeology,1,which.max)]

#as the GEOLOGY class, except for "SS" which just needs 25 % to be the selected class
REC2AreaWeightedGeology$RECGeol <- REC2AreaWeightedGeology$majorityclass
REC2AreaWeightedGeology$RECGeol[REC2AreaWeightedGeology$SS > 0.25] <- "SS"

#Tack these on to the REC2 data
SouthlandREC2$GEOLOGY <- REC2AreaWeightedGeology$RECGeol

#Divide these classes into "Hard" and "Soft"
SouthlandREC2$HardSoft <- "Hard"
SouthlandREC2$HardSoft[which(SouthlandREC2$GEOLOGY %in% c("SS","Al","Pl"))] <- "Soft"

write.table(SouthlandREC2,file.path(DataDirectory,"SouthlandREC2_TK.csv"),row.names = FALSE, quote = FALSE, sep=",")
```
Determination of lakes. This follows the methods of Fraser (2019)
Externally in QGIS
All REC2 watersheds that intersected the LRI TopRock "lak" were identified. These were saved as a csv look-up-table
In this chunk below:
A lake attribute was added to the REC2 Watersheds using the look-up-table
All REC2 reaches downstream of a lake reach were classified as "lake".
Back in QGIS
The REC2 downstream lake reaches were extracted, and their watershed area was intersected with the watershed area of the REC1 reaches with source of flow = "Lk".
This data was saved to a CSV file called "REC2dstLakesMatchedtoREC1SOFLakes.csv"
```{r}
REC2LakeReaches <- read.table(REC2LakeFile,sep=",",stringsAsFactors = FALSE,header = TRUE)
SouthlandREC2$Lakes <- 0
SouthlandREC2$Lakes[which(SouthlandREC2$nzsegment %in% REC2LakeReaches$nzsegment)] <- 1

#Now aggregate them downstream. Note that the nzsegment order MUST match the riverlines data as that is the data that was used to generate the IDSort and Reach data.
SouthlandREC2$dstLakes <- DstAggr_OneVar(IDSort = DownstreamAggregationData[["IDSort"]],Aggrvar = SouthlandREC2$Lakes, Reach = DownstreamAggregationData[["Reach"]], IDnew=seq(1, length(SouthlandREC2$nzsegment),1))

#Save it for later
write.table(SouthlandREC2,file.path(DataDirectory,"SouthlandREC2_TK.csv"),row.names = FALSE, quote = FALSE, sep=",")

#Tack it on to the Watersheds, and save that as well
REC2Watersheds@data$dstLakes <- SouthlandREC2$dstLakes[match(REC2Watersheds@data$nzsegment,SouthlandREC2$nzsegment)]
writeOGR(REC2Watersheds, dsn = file.path(GISDirectory,REC2WaterShedsFile),REC2WaterShedsFile, driver = "ESRI Shapefile",overwrite=TRUE)

```

For the "Natural" Water plan class.
In QGIS
The REC3 watersheds "WaterplanC" attribute was reclassified to a "Natural" attribute, with a "1" if the WaterPlan class was Natural State, and "0" otherwise.
This binary "Natural" attribute was converted to a 30 m raster.
This was repeated in REC1, and the two areas were found to be the same, though REC1 includes islands.
The REC2 watersheds were used to sample the REC1 Natural raster, using the majority of cells in a watershed. (Using Zonal statistics tool)
This class was added to the SouthlandREC2 data
```{r}
# SouthlandREC2 <- join(SouthlandREC2,REC2WaterSheds@data[,c("nzsegment","Naturalmaj")],type="left")
# #rename the "Naturalmaj" column to "Natural"
# names(SouthlandREC2)[which(names(SouthlandREC2) == "Naturalmaj")] <- "Natural"
# 
# #Save it for later
# write.table(SouthlandREC2,file.path(DataDirectory,"SouthlandREC2_TK.csv"),row.names = FALSE, quote = FALSE, sep=",")
```
Alternative Natural determination.
The first approach led to errors where river reaches flowed close by natural areas were getting classed as Natural when really it was supposed to just be the sub-catchments. This is particularly noticeable with the Mataura.
To get around this, instead of allocating the class based on the mode of the class within each reaches watershed, the class was based on the mode of the class at each of the reaches vertices.
QGIS pre-processing
The vertices were created from the REC2 riverlines shapefile
The REC1 Natural 30m raster was sampled at the vertices.
The attributes "nzsegment" and "Natural" were exported to a csv file called "REC2RiverlineVerticesInNaturalArea.csv" in the project's Data directory. The "Natural" attribute was a "1" is natual, empty otherwise.
```{r}
REC2NaturalVertices <- read.table(REC2NaturalRiverVerticesFile,sep=",",header=TRUE)
REC2NaturalVertices$Natural[is.na(REC2NaturalVertices$Natural)] <- 0
#For each nzsegment, find whether or not the majority of its vertices are classed as natural
#Aggregate on NZSegment, returning the majority of Natural
REC2ToNaturalLUT <- aggregate(REC2NaturalVertices$Natural,list(REC2NaturalVertices$nzsegment),FUN= modal)
names(REC2ToNaturalLUT) <- c("nzsegment","Natural")
#Use this look up table to update the "Natural" class in the SouthlandREC2 data frame
SouthlandREC2$Natural <- REC2ToNaturalLUT$Natural[match(SouthlandREC2$nzsegment,REC2ToNaturalLUT$nzsegment)]
write.table(SouthlandREC2,file.path(DataDirectory,"SouthlandREC2_TK.csv"),row.names = FALSE, quote = FALSE, sep=",")
```




Use the REC2 source of flow, GEOLOGY, Natural and Lakes data created using the methods of Fraser (2019) to update the Environment Southland Water Plan classes that were determined through a direct translation from REC1 using the REC2 "NZREACH" attribute. 
It is known that the REC2 to REC1 relationship is imperfect, so combining the two methods should provide the best of both worlds.

```{r}
#Load the REC2 water class file that was derived by the direct translation of the REC1 classes. Call this version Zero.
REC2WaterClassV0 <- read.table(REC2WaterPlanDerivedDirectlyFromREC1, sep=",", header=TRUE, stringsAsFactors = FALSE)

#Create a new version that is to be "corrected", and add the relevant attributes from the SouthlandREC2 data
REC2WaterClassV1 <- join(REC2WaterClassV0,SouthlandREC2[,c("nzsegment","SRC_OF_FLW_new","Natural","HardSoft")],type="left")

##rename the WaterClass from the direct REC1 link as WaterPV0
names(REC2WaterClassV1)[2] <- "WaterPlanV0"

#Load the lakes look up table
LakeReaches <- read.table(REC2LakesCorrectedtoREC1File, sep=",", header=TRUE, stringsAsFactors = FALSE)

#Add on a Lakes attribute
REC2WaterClassV1$Lakes <- 0
REC2WaterClassV1$Lakes[match(LakeReaches$nzsegment,REC2WaterClassV1$nzsegment)] <- 1

#Combine the new source-of-flow attribute with the HardSoft attribute
REC2WaterClassV1$WaterPlanV1 <- REC2WaterClassV1$SRC_OF_FLW_new
REC2WaterClassV1$WaterPlanV1[REC2WaterClassV1$HardSoft == "Hard" & REC2WaterClassV1$SRC_OF_FLW_new == "L"] <- "Lowland hard bed"
REC2WaterClassV1$WaterPlanV1[REC2WaterClassV1$HardSoft == "Soft" & REC2WaterClassV1$SRC_OF_FLW_new == "L"] <- "Lowland soft bed"

#Reclass the lake fed reaches
REC2WaterClassV1$WaterPlanV1[REC2WaterClassV1$Lakes == 1] <- "Lake fed"

#Reclass the natural state reaches
REC2WaterClassV1$WaterPlanV1[REC2WaterClassV1$Natural == 1] <- "Natural State"

#Use the REC1 Water class to allocate the Spring fed
REC2WaterClassV1$WaterPlanV1[REC2WaterClassV1$WaterPlanV0 == "Spring fed"] <- "Spring fed"

#Change the names of the "H" and "M" classes
REC2WaterClassV1$WaterPlanV1[REC2WaterClassV1$WaterPlanV1 == "H"] <- "Hill"
REC2WaterClassV1$WaterPlanV1[REC2WaterClassV1$WaterPlanV1 == "M"] <- "Mountain"

#Save it for later
write.csv(REC2WaterClassV1[,c("nzsegment","WaterPlanV0","WaterPlanV1")],file.path(DataDirectory,"REC2WaterPlanV1.csv"),row.names=FALSE)
```

