---
title: "R Notebook to create a Source-Of-Flow attribute in REC2 which matches the REC1 "SRC_OF_FLW" attribute.
output: html_notebook
---

Tim Kerr
Rainfall.NZ for LWP.

April 2020

This has been prepared based on the report:
Fraser, C., 2009, REC3 ‘Source of Flow’ and ‘Geology’ classifications, Derivation method and comparison with REC1 definitions. Confidential client report for Environment Southland by Land Water People Ltd. LWP Client Report 2019-06. LWP, Christchurch.

Outline
Source of flow is a 5 class classification for rivers where the classes are:
Lowland, Hill country, Mountains, Glacial Mountains and Lakes.
The original source data and methods of preparation have been lost to antiquity, so emulating the classes for new versions of REC is non-trivial.
Caroline Fraser (LWP) developed a method of deriving the classes based on watershed average elevation, upstream average elevation, watershed area, upstream area and stream order, attributes reasonably easily derived for any new REC version.

Caroline developed the process to generate REC3 source of flow.

This script is a replication of Caroline's work except for REC2


set directories and file names
```{r}
ProjectDirectory <- "D:\\Projects\\LWP\\SouthlandRegionalForumModelling"
DataDirectory <- file.path(ProjectDirectory,"Data")
GISDirectory <- file.path(DataDirectory,"GIS")

WatershedsDBFFile <- file.path(GISDirectory,"ES_REC2_Watersheds","ES_REC2_Watersheds.dbf")
RiverlinesDBFFIle <- file.path(GISDirectory,"ES_REC2_Riverlines","ES_REC2_Riverlines.dbf")

REC1ToREC2File <- file.path(GISDirectory,"REC1REC2Intsn","REC1REC2Intsn.dbf")

REC2FUnctions <- file.path(ProjectDirectory,"R","CASM_Southland","GeneralFunctionsForREC2_v10.R")

REC1UtilityFile <- file.path(DataDirectory,"REC1Utility.rdata")  #This contains a dataframe called REC1Utility, which has a whole bunch of REC1 attributes, including "SRC_OF_FLW" which is what we are trying to replicate in REC2

REC1WithESWaterPlanAttributes <- file.path(GISDirectory,"REC1WaterPlan","REC1WaterPlan.dbf")
```


Load libraries and source functions
```{r}
if (!require(foreign)) install.packages("foreign"); library(foreign)                #enables loading of a DBF file
if (!require(dplyr)) install.packages("dplyr"); library(dplyr)                #enables left_join function
#if (!require(rgdal)) install.packages("rgdal"); library(rgdal)                #used for spatial processing
#if (!require(rgeos)) install.packages("rgeos"); library(rgeos)                #used for spatial processing


source(REC2FUnctions)
```

Load the REC2 data Southland
```{r}
#This is an REC data file with up catchment average elevation already calculated.
SouthlandREC2 <- read.table(file.path(DataDirectory,"SouthlandREC2_tk.csv"),sep=",", stringsAsFactors = FALSE, header = TRUE)

REC1ToREC2All <- read.dbf(REC1ToREC2File)

load(REC1UtilityFile)   #This provides the REC1Utility data frame
#Cut it down to Southland
SouthlandREC1 <- REC1Utility[REC1Utility$Region == "S",]
rm(REC1Utility)
SouthlandREC1Extra <- read.dbf(REC1WithESWaterPlanAttributes)

```


If it is necesary to recreate the aggregated upstream mean elevation attribute, that can be done here.
```{r}

#These are the attribute data for the ESRI vector data for the riverlines and the watersheds. They have been pre-processed in QGIS to have mean elevation of each watershed. This was done using focal statistics tool.
WaterSheds <- read.dbf(WatershedsDBFFile)
Riverlines <- read.dbf(RiverlinesDBFFIle)

SouthlandREC2 <- join(Riverlines,WaterSheds[,c("nzsegment","ElevAve")], by="nzsegment")

######################################################################################
#  Downstream Aggregation with area weighting (gives UPST average)                   #
######################################################################################
#This is a slight variation on a disaggregation function commonly used by LWP. I think the difference was required becuase I misused the IDnew parameter to the function.
#I found this function a bit confusing.
#It requires preparation of an IDSort vector, and a Reach vector.
DstAggr_AreaAvg=function(IDSort=NULL,Aggrvar=NULL,segArea=NULL,upstArea=NULL,Reach=Reach,IDnew=NULL){
  
  val<-sort(unique(IDSort))                                 #Determines the order to do the calculations
  OUTPUT<-vector(mode="numeric",length=length(Reach)) *NA   #Initiate output matrix
  OUTPUT[IDnew[which(IDSort==1)]]<-Aggrvar[which(IDSort==1)] #Fill in the 1st order streams (which are just the local values)
  print("Start accumulation....")
  for (i in 2:length(val)){
    index2<-which(IDSort==val[i])
    index<-IDnew[index2]
    for (j in 1:length(index)){
      
      OUTPUT[index[j]]<-(sum(OUTPUT[Reach[[index[j]]]]*upstArea[Reach[[index[j]]]])+Aggrvar[index2[j]]*segArea[index2[j]])/upstArea[index2[j]]  #This ammended version worked
      #OUTPUT[index[j]]<-(sum(OUTPUT[Reach[[index[j]]]]*upstArea[[IDnew[index[j]]]]+Aggrvar[index2[j]]*segArea[index2[j]])/upstArea[index2[j]]  #This version did not work
    } 
  }
  OUTPUT<-OUTPUT[IDnew];OUTPUT[OUTPUT==0]<-NA
  return(OUTPUT)
}

#  Create a list for each reach, which has all of that reach's immediate upstream reaches in it. This is needed to work the downstrea aggregation function above.
# At the same time create a vector of the number of immediately-upstream reach's for each reach.
Reach<-list()
LReach<-seq(1,nrow(SouthlandREC2),1)
for (i in 1:nrow(SouthlandREC2)){
  Reach[[i]]<-which(SouthlandREC2$TO_NODE==SouthlandREC2$FROM_NODE[i])    #Note - to avoid some issues that i encoutered, I would actually make Reach as the ID names rather than just the indexing if i did it again!
  LReach[i]<-length(Reach[[i]])
}

#Go through the reaches from top to bottom and generate "IDSORT"  which gives the order that they shold be processed.
#This takes some time (an hour?!). This is needed to work the downstream aggregation function above
#~~~~~~~~~~~~~~~~~Making IDSort~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
IDRiver < -seq(1,nrow(SouthlandREC2),1)            
IDSort  <- IDRiver*0 
num     <- 1  #First assign a "1" to the most upstream reaches
IDSort[LReach==0]<-num
in1<-sum(IDSort)  
num<-num+1 #Assign the order (IDSort) that the reaches must be calculated in
index  <-which(IDSort==0 & SouthlandREC2$StreamOrde <= num)
index2 <-which(IDSort!=0) #These are the most upstream catchments

while (nrow(SouthlandREC2)-in1>0) {
  ind<-seq(1,length(index),1)
  Lmatch<-unlist(lapply(ind,function(x) length(which(!is.na(match(Reach[[index[x]]],index2))==T))))
  i2<-which(LReach[index]==Lmatch)
  IDSort[index[i2]]<-num
  in1<-in1+length(i2)   
  num<-num+1
  index<-which(IDSort == 0 & SouthlandREC2$StreamOrde <= num)
  index2<-which(IDSort != 0) #These are the most upstream catchments    
  print(in1/nrow(SouthlandREC2)*100)
} 

#Use the downstream aggregation function to get the upstream average elevation for each reach

# accumulate area averaged elevation
SouthlandREC2$upstElev <- DstAggr_AreaAvg(IDSort=IDSort, Aggrvar=SouthlandREC2[, "ElevAve"],segArea = SouthlandREC2$CATAREA,upstArea = SouthlandREC2$CUM_AREA, Reach=Reach, IDnew=seq(1, length(SouthlandREC2$nzsegment),1))

#Accumulate area to test
#SouthlandREC2$AccumArea <- DstAggr_OneVar(IDSort=IDSort, Aggrvar=SouthlandREC2[, "CATAREA"], Reach=Reach, IDnew=seq(1, length(SouthlandREC2$nzsegment),1))

#Save the table for later 
write.table(SouthlandREC2,file.path(DataDirectory,"SouthlandREC2_TK.csv"),row.names = FALSE, quote = FALSE, sep=",")

```


The next step is to establish the elevation threshold that provides the best match for classification to the REC1 source of flow attribute
Externally an REC1 to REC2 allignment has been carried out by intersecting (in QGIS, ignoring the polygons with topological errors) their respective watershed files
The REC1 to REC2 is a many to many relationship, but it is necesary to develop a 1 to 1 relationship. 
This is done in two steps.
1/ For each REC2 ID, select the REC1 ID that intersects with the largest area. This step appears to be missing from Caroline's report.
2/ For each REC1 ID, select the REC2 ID with the largest upstream area.
The REC2 attributes can then be joined to the REC1 ID's.
```{r}
#Pare down the REC1 to REC2 data (many to many) based on the area of intersection to give a REC2 to REC1 1 to many relationship
REC2toManyREC1<-ddply(REC1ToREC2All,.(nzsegment),summarise,NZREACH=NZREACH[which.max(Area)])

#Add upstream area attribute to the REC1-to-REC2 table
REC2toManyREC1PlusCumArea<-join(REC2toManyREC1,SouthlandREC2[,c("nzsegment","CUM_AREA")])

#Select just the largest REC2 for each REC1 to give a 1 to 1 relationship
REC1toREC2<-ddply(REC2toManyREC1PlusCumArea,.(NZREACH),summarise,nzsegment=nzsegment[which.max(CUM_AREA)])

#Tack on all the other REC2 attributes, and the REC1 attributes that will be needed
REC1WithREC2 <- join(REC1toREC2,SouthlandREC2[,c("nzsegment","StreamOrde","CATAREA","CUM_AREA","upstElev")],type="left")
REC1WithREC2 <- left_join(REC1WithREC2, SouthlandREC1[,c("NZReach","SRC_OF_FLW")],by=c("NZREACH"="NZReach"))

#Output the REC1ToREC1 table but only for source of flow of lowland, hill and mountain

REC1WithREC2Output<-REC1WithREC2[REC1WithREC2$SRC_OF_FLW %in% c("L","H","M"),c("NZREACH","StreamOrde","SRC_OF_FLW","CATAREA","CUM_AREA","nzsegment","upstElev")]
write.csv(REC1WithREC2Output,file=file.path(DataDirectory,"REC2toREC1.csv"), row.names = FALSE)
```


Externally (in REC1and REC2.xlsx) the "REC2toREC1.csv" data has been used to develop:
a relationship between the upstream average elevation threshold needed to allocate the Lowland class and log10 of upstream catchment area.
An upstream average elevation threshold for the mountain class.
This was achieved by miniising the difference between the total area of the REC1 "L","H",and "M" Source-of-Flow attributes of each REC2 segment (assigned using the REC1 to REC2 linkage derived above) and the area based on the thresholded upstream area-averaged elevation. This was done for each stream order, then a polynomial relationship found.
This can be used on the REC2 data to generate lowland classes
```{r}
#REC3$LCutoff<-(-1.2141*(log10(REC3$upstArea))^3 + 33.011*(log10(REC3$upstArea))^2 - 261.91*(log10(REC3$upstArea)) + 1045.4) #Original for REC3

SouthlandREC2$LCutoff<-(-1.2709*(log10(SouthlandREC2$CUM_AREA))^3 + 38.021*(log10(SouthlandREC2$CUM_AREA))^2 - 327.11*(log10(SouthlandREC2$CUM_AREA)) + 1264.7) #Original for REC3 
SouthlandREC2$SRC_OF_FLW_new<-"L"
SouthlandREC2$SRC_OF_FLW_new[SouthlandREC2$CatchElev>SouthlandREC2$LCutoff]<-"H"
SouthlandREC2$SRC_OF_FLW_new[SouthlandREC2$ElevAve>980]<-"M"           #The REC3 threshold was 990.

write.table(SouthlandREC2,file.path(DataDirectory,"SouthlandREC2_TK.csv"),row.names = FALSE, quote = FALSE, sep=",")
```


